% --------------------------------------------------
% 6. ROBUSTNESS CHECKS AND EXTENSIONS
% --------------------------------------------------
\section{Robustness Checks and Extensions}

\subsection{Sub-sample Analysis: GC Contenders vs.\ Non-GC Riders}
\begin{itemize}
    \item Present Tables~5a and 5b (separate Cox models for GC contenders and non-GC riders).
    \item Key finding: previous DNF rate is significant in \emph{both} subsamples, but the effect is much stronger for GC contenders (HR $= 2.28$, $p = 0.001$) than for non-GC riders (HR $= 1.47$, $p < 0.001$). This supports heterogeneous cost structures: fragile GC contenders face higher stakes.
    \item The Tour de France protective effect persists for non-GC riders (HR $= 0.866$, $p = 0.005$) but is insignificant for GC contenders, suggesting that the event-value incentive operates primarily through domestiques and support riders.
    \item Include Figure~7 (side-by-side forest plot).
\end{itemize}

\subsection{GC Counterfactual Analysis}
\begin{itemize}
    \item Describe the counterfactual exercise: for each edition where a GC contender abandoned, estimate what the final GC standings would have been had they continued at their last observed pace (Table~6).
    \item This exercise illustrates the economic consequence of selective attrition: abandonment by strong riders reshuffles the final standings, redistributes prize money and UCI points, and affects the information value of the GC classification as a performance signal.
    \item Discuss one or two prominent examples from the data (e.g.\ Wiggins at the 2013 Giro).
    \item Include Figure~8 (counterfactual GC positions bar chart).
\end{itemize}