% --------------------------------------------------
% 7. CONCLUSION
% --------------------------------------------------
\section{Conclusion}
\label{sec:conclusion}

This paper has examined rider abandonment in Grand Tour cycling as an economic decision, using survival analysis methods to study 9,045 rider-race observations across the Tour de France, Giro d'Italia, and Vuelta a Espa\~{n}a from 2010 to 2025. The research question was whether proxy measures of economic incentives and continuation costs can explain the variation in abandonment rates across riders, races, and stages.

The Cox proportional hazard models provide three main findings. First, a rider's historical DNF rate is the strongest predictor of abandonment, with a hazard ratio of 1.549 in the basic model. This is consistent with the interpretation that historical abandonment captures a rider-specific expected continuation cost, whether due to physical fragility, injury history, or the type of rider selected into a Grand Tour starting field. The sub-sample analysis strengthens this result: the effect is substantially larger for GC contenders (HR $= 2.280$) than for non-GC riders (HR $= 1.472$), suggesting heterogeneous cost structures across the two groups. Second, riding in the Tour de France is associated with approximately 14\% lower abandonment hazard than riding in the Vuelta, which is consistent with the event-value hypothesis: the Tour offers higher prize money, more media exposure, and more UCI ranking points, all of which raise the expected return from continued participation. This protective effect is significant for non-GC riders but not for GC contenders, suggesting that the incentive gradient operates primarily through the domestiques and support riders who make up the bulk of the field. Third, mountain stages are associated with a small but significant increase in daily abandonment hazard in the time-varying model, consistent with a marginal-cost-of-effort interpretation: the physical demands of climbing reduce the threshold at which a rider concludes that the cost of continuing exceeds the expected benefit.

Taken together, these findings are consistent with a model in which abandonment is a rational decision shaped by the balance of incentives and costs, in the spirit of the tournament theory framework \parencite{rosen1981superstars, lazear1981rank} and the labour market laboratory perspective \parencite{kahn2000labormarket}. The data cannot establish causality, but the patterns are unlikely to arise from a model in which economic considerations play no role.

Several limitations should be acknowledged. The most important is the absence of direct financial data. No information on rider salaries, team budgets, prize money receipts, or contract structures is available at the rider-race level. The economic interpretation therefore rests on the assumption that the proxy variables used (race identity for event value, GC contender status for tournament incentives, historical DNF rate for continuation costs) are positively correlated with the underlying theoretical constructs. This assumption is plausible but cannot be tested directly. A second limitation is that the GC contender classification is a coarse binary indicator based on past results, which does not capture within-race GC standing. A rider who starts as a GC favourite but crashes on Stage 3 is still classified as a GC contender for the rest of the race, even though their incentive situation has fundamentally changed. Third, the dataset does not distinguish between types of abandonment: crashes, illness, and strategic withdrawal are all coded identically as DNF events. A competing-risks model that separates these causes would provide a more refined picture of the decision process.

Future work could extend the analysis in several directions. Incorporating prize-money or UCI-points data would allow a more direct test of the event-value hypothesis. Adding contract-year indicators, if rider contract data became available, would enable a test of whether riders in the final year of their contract behave differently, as career concerns theory would predict \parencite{boeri2008italianjob}. Extending the sample to one-week stage races would provide a useful comparison: if the abandonment patterns documented here are driven by the unique duration and prestige of Grand Tours, they should be attenuated or absent in shorter events.

Professional cycling offers an unusually transparent window into economic decision-making under physical constraints. The stage-by-stage resolution of the data, the public availability of results, and the clear variation in incentives across races and roles within teams make it a valuable laboratory for studying how individuals respond to costs and rewards in real-time high-stakes environments. The findings of this paper suggest that even the decision to stop racing, which may appear to be purely physical, is shaped by the same forces of incentives, expected returns, and continuation costs that economic theory predicts in other settings.
